### 2022-08-02 ms/ms02_floats.tex
DOC ms

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_vep_consequence.py/missense_variant.png}
%
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_vep_consequence.py/splice_region_variant.png}
%
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_vep_consequence.py/3_prime_UTR_variant.png}
%
\end{subfigure}
%
\caption{\textbf{Location of of variants computed as VEP consequence.} (\textbf{a}) TODO.} \label{fig:gwas_cat_vs_egene_and_sample}
%
\end{figure*}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_violin_egene_per_variant.py/vlnplt.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_violin_etissue_per_variant_egene.py/vlnplt.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_violin_gwas_per_variant_egene_etissue.py/vlnplt.png}
\end{subfigure}
%
\caption{\textbf{TODO.} (\textbf{a}) TODO.} \label{fig:distrib_variant_egene_etissue_gwas}
%
\end{figure*}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
%
\includegraphics[width=\textwidth]{\floatRelativePath/plt_bxplt_remaptf_per_rsid.py/bxplt_remaptf_per_rsid_flank_50.png}
\end{subfigure}
%
\caption{\textbf{Binding of transcription factors in the region (100 kb) around pleiotropic variants.} (\textbf{a}) TODO.} \label{fig:gwas_cat_vs_egene_and_sample}
%
\end{figure*}

>>>>

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_vep_consequence.py/missense_variant.png}
%
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_vep_consequence.py/splice_region_variant.png}
%
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_vep_consequence.py/3_prime_UTR_variant.png}
%
\end{subfigure}
%
\caption{\textbf{Location of of variants computed as VEP consequence.} (\textbf{a}) TODO.} \label{fig:vep_consequence}
%
\end{figure*}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_violin_egene_per_variant.py/vlnplt.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_violin_etissue_per_variant_egene.py/vlnplt.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_violin_gwas_per_variant_egene_etissue.py/vlnplt.png}
\end{subfigure}
%
\caption{\textbf{TODO.} (\textbf{a}) TODO.} \label{fig:freq_gwas_egene_etisue_per_variant}
%
\end{figure*}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
%
\includegraphics[width=\textwidth]{\floatRelativePath/plt_bxplt_remaptf_per_rsid.py/bxplt_remaptf_per_rsid_flank_50.png}
\end{subfigure}
%
\caption{\textbf{Binding of transcription factors in the region (100 kb) around pleiotropic variants.} (\textbf{a}) TODO.} \label{fig:freq_tf_per_variant}
%
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Fig 7: beta
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_violin_beta_pval.py/eqtl_beta.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_violin_beta_pval.py/gwas_beta.png}
\end{subfigure}
%
\caption{\textbf{TODO.} (\textbf{a}) TODO.} \label{fig:beta}
%
\end{figure*}
